Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-13 ms.tex
Putting in core galaxies into table. Break radii still need cleanup

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet,8}$} & {$v_{w}$} & {$\gamma$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm Edd}$} & {$t_{\rm cool}/t_{\rm ff} (r_s)$} & {comments}\\
\hline
0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  energy cons on inner grid\\
1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
  -2 }$ &  TI\\
1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
  3 }$ &  \\
1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &  TI/convergence \\
%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
%  -3 }$ &  TI/convergence\\
1 & 300.0 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
%10^{ -2 }$   & TI/convergence  \\
0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ & TI/convergence \\

@@

\begin{deluxetable}{lllllll}
\tabletypesize{\scriptsize}
%\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pc}
\tablecaption{Core Results \label{tab:sols}}
\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w}$} &
\colhead{$\gamma$} & \colhead{$r_b$} & \colhead{$\dot{M}/\dot{M}_{\rm
Edd}$}  & \colhead{$t_{\rm cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
\startdata
0.01 & 600.0 & 0.1 & 100.0 & $ 3.4 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ &  \\
0.01 & 1200.0 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
0.1 & 1200.0 & 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  \\
\enddata
\end{deluxetable}

>>>>

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet,8}$} & {$v_{w}$} & {$\gamma$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm Edd}$} & {$t_{\rm cool}/t_{\rm ff} (r_s)$} & {comments}\\
\hline
0.01 & 300.0 & 0.8 & N/A & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600.0 & 0.8 & N/A & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200.0 & 0.8 & N/A & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  energy cons on inner grid\\
1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
  -2 }$ &  TI\\
1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
  3 }$ &  \\
1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &  TI/convergence \\
%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
%  -3 }$ &  TI/convergence\\
1 & 300.0 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
%10^{ -2 }$   & TI/convergence  \\
0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
10^{ -2 }$ & TI/convergence \\
0.01 & 1200.0 & 0.1 & N/A & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
10^{ 4 }$ &  rb is unsresolved\\
0.1 & 1200.0 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
  3 }$ &  tried run in which rb=100 pc was resolvedwhat would happen if rb=400 pc?\\

1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{
  2 }$ &  \\
0.01 & 1200.0 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
0.1 & 1200.0 & 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
1 & 1200.0 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
1 & 1200.0 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  convergence\\
1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
1 & 1200.0 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\

@@
